---
title: "Chengyou-Yujie-Community_Contribution_15"
author: "Chengyou Ju, Yujie Wang"
date: "10/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This Rmd file is created by Chengyou Ju (UNI: cj2624) and Yujie Wang (UNI: yw3442) for STAT GR5702 Community Contribution Group 15.

In this file, we will provide a tutorial on how to draw Wordcloud graphs using the `wordcloud2` package in R. 

The dataset in this project are from the **demoFreq** package.

## 1. Introduction

A Wordcloud is a visual representation of text data. Wordclouds are useful for quickly perceiving the most prominent terms, which makes them widely used in media and well understood by the public. 

There are two packages in R that can help us draw a wordcloud. `wordcloud` is the basic package to build the graph, while `wordcloud2` package allows more customization. In our demo, we will focus on the `wordcloud2` package, which is more widely used.

## 2. Demo of `wordcloud2` Package

For our demo, we will use a built-in dataset `demoFreq`, which has 1011 observations of 2 variables, words and frequancy.
```{r}
head(demoFreq)
```

### 2.0 Basic Wordcloud Graph
Building a wordcloud graph is simple. We can use the `wordcloud2` package directly after successfully installing it.
```{r}
library(wordcloud2)
wordcloud2(data = demoFreq)
```

### 2.1 Font Size
We can also modify the font size of the graph.
```{r}
wordcloud2(data = demoFreq, size = 0.5)
```
```{r}
wordcloud2(data = demoFreq, size = 1.5)
```

### 2.2 Color and Background Color
The word color can be changed using the "color" argument, while the background color can be changed with "backgroundColor".
```{r}
wordcloud2(demoFreq, color = 'random-dark')
```
```{r}
wordcloud2(demoFreq, color = 'random-light')
```
```{r}
wordcloud2(demoFreq, color = 'random-light', backgroundColor = "black")
```
```{r}
wordcloud2(demoFreq, color = rep_len(c("skyblue", "blue"), nrow(demoFreq)))
```

### 2.3 Shape
We can also customize the shape of a wordcloud using the "shape" argument. Here are some examples.
```{r}
wordcloud2(demoFreq, size = 0.5, shape = 'star')
```
```{r}
wordcloud2(demoFreq, size = 0.5, shape = 'pentagon')
```

```{r}
letterCloud(demoFreq, word = "R", color = "random-light", backgroundColor = "black")
can also do rotation on the wordcloud graph.
```{r}
wordcloud2(demoFreq, minRotation = -pi/6, maxRotation = -pi/6, rotateRatio = 1)
```

### 2.5 Language
We can draw a wordcloud graph of words in Chinese.
```{r}
wordcloud2(demoFreqC, fontFamily = "????????????", color = "random-light", backgroundColor = "black")
```